\LARGE \bf Eye tracking with Educational Robots: A Cautionary Tale

### 2014-09-30 paper.tex
Figure updates and remove ref 20

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{thymio}
    \caption{\small \textbf{Thymio II}: the proximity sensors were used to
    detect the obstacle based on the reflectance of the material. The sensor
    data was shown as a proportion of the circle lit using the LEDs on top of the
    robot.}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{playground}
    \caption{\small Basic playground for the experiment. The fiducial markers
    are used for automatic localization of the gaze pointers on the observation
    video.}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{expe}
    \caption{\small Experimental setup for observation phase. The observation
    video is recorded from the video camer in the front of the eye tracker (in
    the lop-left corner).}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{res1}
    \caption{Average fixation duration on the robot ~during the observation phase
    vs.~Condition}
    \label{res1}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{res2}
    \caption{First improvement vs.~experimental condition}
    \label{res2}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{res3}
    \caption{Average fixation duration on the reference side during the
    interaction phase vs.~Condition}
    \label{res3}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{res4}
    \caption{First improvement in centimeters ($y$-axis) vs.~number of fixations
    on reference side ($x$-axis) during the interaction phase.}
    \label{res4}
\end{figure}

@@

Another plausible explanation for the participants in NONE and RANDOM condition
being better performers than the TRUE condition during the interaction phase
comes from the transparency of the robot's behavior~\cite{??}. The robot's
behavior was not at all transparent in the former two conditions. This might
have caused the participants to put more effort in understanding the behavior.
Therefore, they performed better.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{thymio0}
    \caption{\small \textbf{Thymio II}: the proximity sensors were used to
    detect the obstacle based on the reflectance of the material. The sensor
    data was shown as a proportion of the circle lit using the LEDs on top of the
    robot.}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{maze}
    \caption{\small Basic playground for the experiment. The fiducial markers
    are used for automatic localization of the gaze pointers on the observation
    video.}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{setup0}
    \caption{\small Experimental setup for observation phase. The observation
    video is recorded from the video camer in the front of the eye tracker (in
    the lop-left corner).}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{meanPlotFixRobo.pdf}
    \caption{Average fixation duration on the robot ~during the observation phase
    vs.~Condition}
    \label{res1}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{meanPlotFirstImprove.pdf}
    \caption{First improvement vs.~experimental condition}
    \label{res2}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{meanPlotFixRreference.pdf}
    \caption{Average fixation duration on the reference side during the
    interaction phase vs.~Condition}
    \label{res3}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{corPlotFirstImprove.pdf}
    \caption{First improvement in centimeters ($y$-axis) vs.~number of fixations
    on reference side ($x$-axis) during the interaction phase.}
    \label{res4}
\end{figure}

@@

Another plausible explanation for the participants in NONE and RANDOM condition
being better performers than the TRUE condition during the interaction phase
comes from the transparency of the robot's behavior. The robot's
behavior was not at all transparent in the former two conditions. This might
have caused the participants to put more effort in understanding the behavior.
Therefore, they performed better.
